### 2023-05-05 paper/localpsf.tex
a little bit of cleanup and consistently using \| instead of || for indicating norms

We solve the ice sheet inverse problem with an inexact Newton preconditioned
conjugate gradient (PCG) scheme and a globalizing Armijo line search~\cite{NocedalWright99}. The Newton updates,
$\bm{\searchdir}_k$, are obtained by solving 
%
\begin{equation}
	\label{eq:newton_system}
	\bm{H} \bm{\searchdir}_k = - \bm{g}_k \qquad \text{or} \qquad \bm{H}_\text{gn} \bm{\searchdir}_k = - \bm{g}_k,
\end{equation}
%
wherein we choose the initial guess as the discretization of the constant
function $q_0$. Here $\bm{g}_k$, $\bm{H}$ and $\bm{H}_\text{gn}$ are
the discretized gradient, Hessian, and Gauss-Newton Hessian of the
inverse problem cost function, respectively.
%The Gauss-Newton Hessian is Hessian of $J$, except in the data misfit, $J_d$, the nonlinear mapping $\basalfriction \mapsto \tangentop \velocity$ is replaced by its local linearization at $\basalfriction_k$.
To ensure positive definiteness of the Hessian we use
$\bm{H}_\text{gn}$ for the first five iterations, and $\bm{H}$ for all
subsequent iterations. The Newton iterations are terminated when
$||\bm{g}_k||/||\bm{g}_0|| < 10^{-8}$. Systems~\eqref{eq:newton_system} are solved inexactly using an inner PCG
iteration, which terminates when the norm of the linear system residual is less than $\min \left(0.5,
\sqrt{||\bm{g}_k||}\right)||\bm{g}_k||$. The advection-diffusion inverse problem is linear, so Newton's method converges in one iteration. In this case the Newton linear system,~\eqref{eq:newton_system}, is solved using PCG with a fixed tolerance which is specified in Section~\ref{sec:adv}.

@@

\begin{figure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{mtrue_withColorBar.png}
		\caption{$\basalfriction_\text{true}$.}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{trueVelocity2_glyphs.png}
		\caption{$\velocity_\text{true}$.}
	\end{subfigure}
	\caption{True parameter, $\basalfriction_\text{true}$, (left) and true velocity $\velocity_\text{true}$ (right). In the right plot, arrows indicate the direction of $\velocity_\text{true}$ and color indicates the magnitude of $\velocity_\text{true}$.}
	\label{fig:true_beta_u}
\end{figure}

@@

%	J_d(\basalfriction) := \frac{1}{2}\int_{\Gamma_{t}}||\observations_\text{obs} - \tangentop\velocity||_{2}^{2}\,dS.

@@

%	\int_{\Gamma_{t}}||\observations_\text{obs} - \tangentop\velocity||_{2}^{2}\,dS = \int_{\Gamma_{t}}||\xi||_{2}^{2}\,dS.

@@

	\caption{The log basal sliding parameter computed from the PDE-constrained optimization problem with noise levels: $25\%$ (left), $11\%$ (second from left), $5.0\%$ (third from left), $2.2\%$ (fourth from left), and $1.0\%$ (right). The PSF (5) preconditioner is constructed between Newton iterations 3 and 4. \todo{remove reference to newon iterates figure as this figure has a new significance}}

@@

\begin{table}
	{\small
		\begin{center}
			\begingroup
			\setlength{\tabcolsep}{3pt}
			\renewcommand{\arraystretch}{1.1}
			\begin{tabular}{c| c c c | c c c | c c c}
				&  \multicolumn{3}{|c|}{PSF (5)} & \multicolumn{3}{|c|}{REG} & \multicolumn{3}{|c}{NONE} \\
				\hline
				Iter & 
				\#CG & \#Stokes & $||\bm{g}||$ & 
				\#CG & \#Stokes & $||\bm{g}||$ & 
				\#CG & \#Stokes & $||\bm{g}||$ \\
				0 &
				1 & 4 & 2.0e+7 &
				1 & 4 & 2.0e+7 &
				1 & 4 & 2.0e+7 \\
				1 &
				2 & 6 & 5.8e+6 &
				2 & 6 & 7.9e+6 &
				2 & 6 & 5.8e+6 \\
				2 &
				4 & 10 & 2.4e+6 &
				5 & 12 & 3.9e+6 &
				4 & 10 & 2.4e+6 \\
				3 &
				2 & 6+22 & 5.8e+5 &
				13 & 28 & 1.6e+6 &
				13 & 28 & 5.8e+5 \\
				4 &
				5 & 12 & 5.6e+4 &
				42 & 86 & 4.8e+5 &
				33 & 68 & 9.1e+4 \\
				5 &
				10 & 22 & 3.5e+3 &
				84 & 170 & 7.7e+4 &
				57 & 116 & 6.2e+3 \\
				6 &
				14 & 30 & 2.7e+1 &
				125 & 252 & 5.0e+3 &
				76 & 154 & 1.1e+2 \\
				7 &
				0 & 2 & 4.1e-2 &
				194 & 390 & 7.9e+1 &
				117 & 236 & 2.3e-1 \\
				8 & 
				--- & --- & --- &
				0 & 2 & 1.6e-1 &
				0 & 2 & 4.1e-2 \\
				\hline
				Total & 
				38 & 114 & --- &
				466 & 950 & --- &
				303 & 624 & --- \\
			\end{tabular}
			\endgroup
		\end{center}
	}
	\caption{Convergence history for solving the Stokes inverse problem using preconditioned inexact Newton PCG. Preconditioners shown are our method with five batches (PSF (5)) constructed at the third iteration, regularization preconditioning (REG), and no preconditioning (NONE). Columns titled \#CG show the number of PCG iterations used to solve the Newton system for $\bm{\widehat{\basalfriction}}_k$. Columns titled $||\bm{g}||$ show the $l^2$ norm of the gradient at $\bm{\basalfriction}_k$. Columns titled \#Stokes show the total number of Stokes PDE solves performed in each Newton iteration. This consists of Stokes solves for $u$ performed during the linesearch going from $\bm{\basalfriction}_{k-1}$ to $\bm{\basalfriction}_k$, plus one adjoint Stokes solve to compute the gradient at $\bm{\basalfriction}_k$, plus one incremental forward and one incremental adjoint Stokes solve per PCG iteration for solving the Newton system. In the PSF (5) portion of row 3, we write $6+22$ to indicate that 6 Stokes solves were used during the standard course of the iteration, and 22 Stokes solves were used to build the PSF (5) preconditioner.}
	\label{tab:newton_convergence_table}
\end{table}

@@

		ylabel={$||\bm{x}_k-\bm{x}_{\text{true}}||/||\bm{x}_{\text{true}}||$},

@@

		ylabel near ticks, %ylabel shift={-6pt},

@@

	Here we use $\gamma=7.3 \times 10^3$, which is determined by the Morozov discrepancy principle. Results in these figures are shown for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), regularization preconditioning (REG), and no preconditioning (NONE). The preconditioner is constructed using $\bm{H}_\text{gn}$.

@@

\begin{figure}
	\begin{center}
			\begingroup
			\setlength{\tabcolsep}{4pt}
			\renewcommand{\arraystretch}{1.25}
			\begin{tabular}{c| c c c c c}
				noise    & \multicolumn{5}{c}{COND$(\bm{\preconditioner}^{-1} \bm{H})$ } \\ \cline{2-6}
				level    & REG     &	NONE  & PSF $(1)$ & PSF $(5)$ & PSF $(25)$ \\ \hline 
				$25\%$   & 1.68e+3 & 2.16e+3  & 1.37e+0   & 1.30e+0   & 1.21e+0    \\ 
				$11\%$   & 9.19e+3 & 9.08e+2  & 1.85e+0   & 1.49e+0   & 1.27e+0    \\   
				$5.0\%$  & 3.66e+4 & 4.67e+2  & 3.46e+0   & 2.62e+0   & 1.91e+0    \\ 
				$2.2\%$  & 1.41e+5 & 8.25e+2  & 1.16e+1   & 4.99e+0   & 3.20e+0    \\  
				$1.0\%$  & 6.06e+5 & 1.70e+3  & 3.44e+1   & 5.38e+1   & 7.06e+0    \\   
			\end{tabular}
			\endgroup
		\end{center}
	\caption{Condition number for $\bm{\preconditioner}^{-1} \bm{H}$ for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), no preconditioner (NONE) and regularization (REG). All operators are evaluated at the $\bm{\basalfriction}$ that solves the inverse problem for 
	the regularization value $\gamma$ as determined by noise level by means of the Morozov discrepancy principle.}
	\label{fig:condition_number}
\end{figure}

@@

\begin{figure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		ymode=log,
		ymin=1e-11,
		ymax=2,
		xmax=750,
		axis x line*=bottom,
		axis y line*=left,
		xtick={0, 200, 400, 600},
		xlabel={CG iteration},
		ylabel={$||\bm{b}-\bm{H} \bm{x}_k||/||\bm{b}||$},
		title={CG convergence},
		legend style={at={(1.1,1)},anchor=north east},
		%legend pos=north east,
		legend style={font=\small}
		]
		\addlegendentry{Reg}
		\addplot[dotted, line width=0.5mm] table {cg_relres_reg.dat};
		\addlegendentry{None}
		\addplot[dash dot, line width=0.5mm] table {cg_relres_none.dat};
		\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table {cg_relres_p1.dat};
		\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table {cg_relres_p5.dat};
		\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table {cg_relres_p25.dat};
		\end{axis}
		\end{tikzpicture}
		\caption{}
		\label{fig:adv_cg_convergence}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		xmode=log,
		ymode=log,
		xlabel={$\gamma$, regularization parameter},
		ylabel={\# of CG iterations},
		axis y line*=right,
		axis x line*=bottom,
		ylabel near ticks, yticklabel pos=right,
		%ylabel near ticks, ylabel shift={-6pt},
		%legend pos=north east,
		title={Regularization robustness}
		%title={CG iterations to achieve $||H x-b||/||b||<10^{-6}$}
		]
		%\addlegendentry{None}
		\addplot[dash dot, line width=0.5mm] table[x=gamma, y=none] {CGitsvsGamma.dat};
		%\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=gamma, y=reg] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table[x=gamma, y=psf1] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table[x=gamma, y=psf5] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table[x=gamma, y=psf25] {CGitsvsGamma.dat};
		\end{axis}
		\end{tikzpicture}
		\caption{}
		\label{fig:adv_kappa_sweep}
	\end{subfigure}
	\caption{Left (\ref{fig:adv_cg_convergence}) shows the convergence history for solving $\bm{H} \bm{x} = \bm{b}$ using PCG, where $\bm{b}$ has i.i.d. random entries drawn from the standard normal distribution. BLAH BLAH BLAH
		%		The y-axis is $||b-Hx_k||/||b||$, where $x_k$ is the $k$th PCG iterate. 
		Here we use $\gamma=9999 \times 10^9$, which is determined by the Morozov discrepancy principle. Right (\ref{fig:adv_kappa_sweep}) shows the number of PCG iterations required to achieve $||\bm{b}-\bm{H} \bm{x}_k||/||\bm{b}|| < 10^{-6}$, where $\bm{x}_k$ is the $k$th PCG iterate, for a range of different $\kappa$. Results in these figures are shown for our preconditioner with 5, 15, and 30 batches (PSF (5), PSF (15), and PSF(30), respectively), regularization preconditioning (REG), and no preconditioning (NONE). The preconditioner is constructed using $\bm{H}_\text{gn}$.}
	\label{fig:adv_krylov_convergence}
\end{figure}

>>>>

We solve the ice sheet inverse problem with an inexact Newton preconditioned
conjugate gradient (PCG) scheme and a globalizing Armijo line search~\cite{NocedalWright99}. The Newton updates,
$\bm{\searchdir}_k$, are obtained by solving 
%
\begin{equation}
	\label{eq:newton_system}
	\bm{H} \bm{\searchdir}_k = - \bm{g}_k \qquad \text{or} \qquad \bm{H}_\text{gn} \bm{\searchdir}_k = - \bm{g}_k,
\end{equation}
%
wherein we choose the initial guess as the discretization of the constant
function $q_0$. Here $\bm{g}_k$, $\bm{H}$ and $\bm{H}_\text{gn}$ are
the discretized gradient, Hessian, and Gauss-Newton Hessian of the
inverse problem cost function, respectively.
%The Gauss-Newton Hessian is Hessian of $J$, except in the data misfit, $J_d$, the nonlinear mapping $\basalfriction \mapsto \tangentop \velocity$ is replaced by its local linearization at $\basalfriction_k$.
To ensure positive definiteness of the Hessian we use
$\bm{H}_\text{gn}$ for the first five iterations, and $\bm{H}$ for all
subsequent iterations. The Newton iterations are terminated when
$\|\bm{g}_k\|/\|\bm{g}_0\| < 10^{-8}$. Systems~\eqref{eq:newton_system} are solved inexactly using an inner PCG
iteration, which terminates when the norm of the linear system residual is less than $\min \left(0.5,
\sqrt{\|\bm{g}_k\|}\right)\|\bm{g}_k\|$. The advection-diffusion inverse problem is linear, so Newton's method converges in one iteration. In this case the Newton linear system,~\eqref{eq:newton_system}, is solved using PCG with a fixed tolerance which is specified in Section~\ref{sec:adv}.

@@

\begin{figure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{mtrue_withColorBar.png}
		\caption{$\basalfriction_\text{true}$.}
		\label{fig:true_beta}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{trueVelocity2_glyphs.png}
		\caption{$\velocity_\text{true}$.}
	\end{subfigure}
	\caption{True parameter, $\basalfriction_\text{true}$, (left) and true velocity $\velocity_\text{true}$ (right). In the right plot, arrows indicate the direction of $\velocity_\text{true}$ and color indicates the magnitude of $\velocity_\text{true}$.}
	\label{fig:true_beta_u}
\end{figure}

@@

%	J_d(\basalfriction) := \frac{1}{2}\int_{\Gamma_{t}}\|\observations_\text{obs} - \tangentop\velocity\|_{2}^{2}\,dS.

@@

%	\int_{\Gamma_{t}}\|\observations_\text{obs} - \tangentop\velocity\|_{2}^{2}\,dS = \int_{\Gamma_{t}}\|\xi\|_{2}^{2}\,dS.

@@

	\caption{The log basal sliding parameter, with colorscale as in Figure~\ref{fig:true_beta}, computed from the PDE-constrained optimization problem with noise levels: $25\%$ (left), $11\%$ (second from left), $5.0\%$ (middle), $2.2\%$ (second from right), and $1.0\%$ (right). \todo{remove reference to newon iterates figure as this figure has a new significance}}

@@

\begin{table}
	{\small
		\begin{center}
			\begingroup
			\setlength{\tabcolsep}{3pt}
			\renewcommand{\arraystretch}{1.1}
			\begin{tabular}{c| c c c | c c c | c c c}
				&  \multicolumn{3}{|c|}{PSF (5)} & \multicolumn{3}{|c|}{REG} & \multicolumn{3}{|c}{NONE} \\
				\hline
				Iter & 
				\#CG & \#Stokes & $\|\bm{g}\|$ & 
				\#CG & \#Stokes & $\|\bm{g}\|$ & 
				\#CG & \#Stokes & $\|\bm{g}\|$ \\
				0 &
				1 & 4 & 2.0e+7 &
				1 & 4 & 2.0e+7 &
				1 & 4 & 2.0e+7 \\
				1 &
				2 & 6 & 5.8e+6 &
				2 & 6 & 7.9e+6 &
				2 & 6 & 5.8e+6 \\
				2 &
				4 & 10 & 2.4e+6 &
				5 & 12 & 3.9e+6 &
				4 & 10 & 2.4e+6 \\
				3 &
				2 & 6+22 & 5.8e+5 &
				13 & 28 & 1.6e+6 &
				13 & 28 & 5.8e+5 \\
				4 &
				5 & 12 & 5.6e+4 &
				42 & 86 & 4.8e+5 &
				33 & 68 & 9.1e+4 \\
				5 &
				10 & 22 & 3.5e+3 &
				84 & 170 & 7.7e+4 &
				57 & 116 & 6.2e+3 \\
				6 &
				14 & 30 & 2.7e+1 &
				125 & 252 & 5.0e+3 &
				76 & 154 & 1.1e+2 \\
				7 &
				0 & 2 & 4.1e-2 &
				194 & 390 & 7.9e+1 &
				117 & 236 & 2.3e-1 \\
				8 & 
				--- & --- & --- &
				0 & 2 & 1.6e-1 &
				0 & 2 & 4.1e-2 \\
				\hline
				Total & 
				38 & 114 & --- &
				466 & 950 & --- &
				303 & 624 & --- \\
			\end{tabular}
			\endgroup
		\end{center}
	}
	\caption{Convergence history for solving the Stokes inverse problem using preconditioned inexact Newton PCG. Preconditioners shown are our method with five batches (PSF (5)) constructed at the third iteration, regularization preconditioning (REG), and no preconditioning (NONE). Columns titled \#CG show the number of PCG iterations used to solve the Newton system for $\bm{\widehat{\basalfriction}}_k$. Columns titled $\|\bm{g}\|$ show the $l^2$ norm of the gradient at $\bm{\basalfriction}_k$. Columns titled \#Stokes show the total number of Stokes PDE solves performed in each Newton iteration. This consists of Stokes solves for $u$ performed during the linesearch going from $\bm{\basalfriction}_{k-1}$ to $\bm{\basalfriction}_k$, plus one adjoint Stokes solve to compute the gradient at $\bm{\basalfriction}_k$, plus one incremental forward and one incremental adjoint Stokes solve per PCG iteration for solving the Newton system. In the PSF (5) portion of row 3, we write $6+22$ to indicate that 6 Stokes solves were used during the standard course of the iteration, and 22 Stokes solves were used to build the PSF (5) preconditioner.}
	\label{tab:newton_convergence_table}
\end{table}

@@

		ylabel={$\|\bm{x}_k-\bm{x}_{\text{true}}\|/\|\bm{x}_{\text{true}}\|$},

@@

		ylabel near ticks, ylabel shift={-6pt},

@@

	Here we use $\gamma=7.3 \times 10^3$, which is determined by the Morozov discrepancy principle when using $5\%$ noise. Results in these figures are shown for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), regularization preconditioning (REG), and no preconditioning (NONE). The preconditioner is constructed using $\bm{H}_\text{gn}$.

@@

\begin{figure}
	\begin{center}
			\begingroup
			\setlength{\tabcolsep}{4pt}
			\renewcommand{\arraystretch}{1.25}
			\begin{tabular}{c| c c c c c}
				noise    & \multicolumn{5}{c}{COND$(\bm{\preconditioner}^{-1} \bm{H})$ } \\ \cline{2-6}
				level    & REG     &	NONE  & PSF $(1)$ & PSF $(5)$ & PSF $(25)$ \\ \hline 
				$25\%$   & 1.68e+3 & 2.16e+3  & 1.37e+0   & 1.30e+0   & 1.21e+0    \\ 
				$11\%$   & 9.19e+3 & 9.08e+2  & 1.85e+0   & 1.49e+0   & 1.27e+0    \\   
				$5.0\%$  & 3.66e+4 & 4.67e+2  & 3.46e+0   & 2.62e+0   & 1.91e+0    \\ 
				$2.2\%$  & 1.41e+5 & 8.25e+2  & 1.16e+1   & 4.99e+0   & 3.20e+0    \\  
				$1.0\%$  & 6.06e+5 & 1.70e+3  & 3.44e+1   & 5.38e+1   & 7.06e+0    \\   
			\end{tabular}
			\endgroup
		\end{center}
	\caption{Condition number for $\bm{\preconditioner}^{-1} \bm{H}$ for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), no preconditioner (NONE) and regularization (REG). All operators are evaluated at the $\bm{\basalfriction}$ that solves the inverse problem for 
	the regularization value $\gamma$ as determined by the respective noise level and the Morozov discrepancy principle.}
	\label{fig:condition_number}
\end{figure}

@@

\begin{figure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		ymode=log,
		ymin=1e-11,
		ymax=2,
		xmax=750,
		axis x line*=bottom,
		axis y line*=left,
		xtick={0, 200, 400, 600},
		xlabel={CG iteration},
		ylabel={$\|\bm{b}-\bm{H} \bm{x}_k\|/\|\bm{b}\|$},
		title={CG convergence},
		legend style={at={(1.1,1)},anchor=north east},
		%legend pos=north east,
		legend style={font=\small}
		]
		\addlegendentry{Reg}
		\addplot[dotted, line width=0.5mm] table {cg_relres_reg.dat};
		\addlegendentry{None}
		\addplot[dash dot, line width=0.5mm] table {cg_relres_none.dat};
		\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table {cg_relres_p1.dat};
		\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table {cg_relres_p5.dat};
		\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table {cg_relres_p25.dat};
		\end{axis}
		\end{tikzpicture}
		\caption{}
		\label{fig:adv_cg_convergence}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		xmode=log,
		ymode=log,
		xlabel={$\gamma$, regularization parameter},
		ylabel={\# of CG iterations},
		axis y line*=right,
		axis x line*=bottom,
		ylabel near ticks, yticklabel pos=right,
		%ylabel near ticks, ylabel shift={-6pt},
		%legend pos=north east,
		title={Regularization robustness}
		%title={CG iterations to achieve $\|H x-b\|/\|b\|<10^{-6}$}
		]
		%\addlegendentry{None}
		\addplot[dash dot, line width=0.5mm] table[x=gamma, y=none] {CGitsvsGamma.dat};
		%\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=gamma, y=reg] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table[x=gamma, y=psf1] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table[x=gamma, y=psf5] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table[x=gamma, y=psf25] {CGitsvsGamma.dat};
		\end{axis}
		\end{tikzpicture}
		\caption{}
		\label{fig:adv_kappa_sweep}
	\end{subfigure}
	\caption{Left (\ref{fig:adv_cg_convergence}) shows the convergence history for solving $\bm{H} \bm{x} = \bm{b}$ using PCG, where $\bm{b}$ has i.i.d. random entries drawn from the standard normal distribution. BLAH BLAH BLAH
		%		The y-axis is $\|b-Hx_k\|/\|b\|$, where $x_k$ is the $k$th PCG iterate. 
		Here we use $\gamma=9999 \times 10^9$, which is determined by the Morozov discrepancy principle. Right (\ref{fig:adv_kappa_sweep}) shows the number of PCG iterations required to achieve $\|\bm{b}-\bm{H} \bm{x}_k\|/\|\bm{b}\| < 10^{-6}$, where $\bm{x}_k$ is the $k$th PCG iterate, for a range of different $\kappa$. Results in these figures are shown for our preconditioner with 5, 15, and 30 batches (PSF (5), PSF (15), and PSF(30), respectively), regularization preconditioning (REG), and no preconditioning (NONE). The preconditioner is constructed using $\bm{H}_\text{gn}$.}
	\label{fig:adv_krylov_convergence}
\end{figure}
